Bioverse: Origins of Life

### 2024-07-02 src/tex/ms.tex
reorder discussion
write first discussion section

%! suppress = GroupedSubSupScript
%! suppress = Ellipsis
% Define document class
%\documentclass[twocolumn,twocolappendix,linenumbers]{aastex631}
\documentclass[modern,linenumbers]{aastex631}

@@

\section{Methods}
\label{sec:hypotests}
\todo[inline]{Briefly introduce Bayesian model comparison, then present the particular hypotheses in their mathematical form.}

@@

\section{Discussion}
\label{sec:discussion}
%''Which natural processes best explain how living matter spontaneously appears from nonliving matter?''~\citep{Malaterre2022}
%WE consider life ``as we know it''

@@

\subsection{Constraining power for the origins of life as a function of biosignature location}
\todo[inline]{How does the location of biosignature detections impact the credibility of OOL scenarios?}
\todo[inline]{biosignature on M~dwarf planet vs. FGK: Impact on UV flux requirement?}
\subsubsection{Sampling strategy for testing a predicted minimum \gls{NUV} flux}
We show in Sect.~\ref{sec:results} that the constraining power for testing the hypothesis of a minimum past \gls{NUV} flux required for abiogenesis is sensitive on the occurrence of life, the value of this threshold flux, the sample size, and the distribution of sampled past \gls{NUV} fluxes.
In particular the last parameter offers an opportunity to optimize the survey strategy: Although constraints on a planet's UV history have generally large uncertainties~\citep[e.g.,][]{Richey-Yowell2023}, the likely maximum flux of a planet can be inferred and used as a proxy.
Sampling more extreme (low and high) values for the maximum flux increases the probability of obtaining true strong evidence for the hypothesis.
For large sample sizes $\gtrsim 200$, this strategy can push this probability into the \SI{90}{\percent} range.
\todo[inline]{and what about the probability of getting true strong evidence for H0?}

>>>>

%! suppress = GroupedSubSupScript
%! suppress = Ellipsis
% Define document class
\documentclass[twocolumn,twocolappendix,linenumbers]{aastex631}
%\documentclass[modern,linenumbers]{aastex631}

@@

\section{Methods}
\label{sec:hypotests}
%\todo[inline]{Briefly introduce Bayesian model comparison, then present the particular hypotheses in their mathematical form.}

@@

\section{Discussion}
\label{sec:discussion}
%''Which natural processes best explain how living matter spontaneously appears from nonliving matter?''~\citep{Malaterre2022}
%WE consider life ``as we know it''
\subsection{Constraining power for the origins of life as a function of biosignature location}
\todo[inline]{How does the location of biosignature detections impact the credibility of OOL scenarios?}
\todo[inline]{biosignature on M~dwarf planet vs. FGK: Impact on UV flux requirement?}
The cyanosulfidic scenario, in particular its predicted existence of a minimum \gls{NUV} flux required for prebiotic chemistry, offers an opportunity to test an origins of life hypothesis with a statistical transit survey sampling planets with varying \gls{NUV} flux histories.
It comes to no surprise that the success rate of such a test is sensitive to the sample size of the survey and to the occurrence of life on temperate exoplanets.
As we have shown, the statistical power of this test also depends on the distribution of past \gls{NUV} fluxes in the sample and on the required threshold flux.
Optimizing the survey to sample a wide range of NUV flux values, particularly at the extremes, can enhance the likelihood of obtaining strong evidence for or against the hypothesis.
Intermediate values of the threshold \gls{NUV} flux are more likely to yield strong evidence than extreme values, as the dataset under the alternative hypothesis $H_1$ differs more from the null hypothesis in this case while still being sufficiently populated.
The required threshold flux is, of course, a priori unknown and we cannot influence it.
If, however, better theoretical predictions for the required \gls{NUV} flux for abiogenesis become available, the survey strategy can be further optimized, for instance by targeting planets that are estimated to have received a \gls{NUV} flux slightly below and above this threshold.

An interesting  aspect lies in the distribution of host star spectral types:
Under the \gls{NUV} hypothesis, the occurrence of life is expected to correlate with the host star's spectral type, with late-type M~dwarfs being favored due to their higher \gls{NUV} fluxes in the \gls{HZ}~\citep{Richey-Yowell2023}.
However, the distribution of maximum past \gls{NUV} fluxes in this sample is narrow in this sample, which may limit the constraining power of the survey depending on the (unknown) threshold \gls{NUV} flux.
An M~dwarf sample may help to test the high \gls{NUV} flux end of the hypothesis; a higher occurrence of biosignatures here would support the hypothesis that a higher NUV flux is beneficial or necessary for life.

FGK stars, on the other hand, show a wider distribution of maximum past \gls{NUV} fluxes in the \gls{HZ}, which may increase the likelihood of obtaining strong evidence for or against the hypothesis.
With this sample, the survey will be more sensitive to the low \gls{NUV} flux end of the hypothesis.
A lack of biosignatures on these planets would support the \gls{NUV} hypothesis, whereas their presence might suggest that lower NUV fluxes are also sufficient for abiogenesis or indicate different abiogenic pathways. CITE

@@

\subsubsection{Sampling strategy for testing a predicted minimum \gls{NUV} flux}
We show in Sect.~\ref{sec:results} that the constraining power for testing the hypothesis of a minimum past \gls{NUV} flux required for abiogenesis is sensitive on the occurrence of life, the value of this threshold flux, the sample size, and the distribution of sampled past \gls{NUV} fluxes.
In particular the last parameter offers an opportunity to optimize the survey strategy: Although constraints on a planet's UV history have generally large uncertainties~\citep[e.g.,][]{Richey-Yowell2023}, the likely maximum flux of a planet can be inferred and used as a proxy.
Sampling more extreme (low and high) values for the maximum flux increases the probability of obtaining true strong evidence for the hypothesis.
For large sample sizes $\gtrsim 200$, this strategy can push this probability into the \SI{90}{\percent} range.
\todo[inline]{and what about the probability of getting true strong evidence for H0?}
